Clustering/Orthofinder analysis

### 2022-02-25 analysis/Orthofinder.Rmd
Fix bug in the very last lines

groups_lost_in_A_antarctica <- setdiff(groups_in_all_seagrasses, big_list[['A. antarctica']])
genes_lost_in_A_antarctica <- gene_per_spec %>% 
  filter(name == 'A. antarctica', Orthogroup %in% groups_lost_in_A_antarctica) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_P_australis <- setdiff(groups_in_all_seagrasses, big_list[['P. australis']])
genes_lost_in_P_australis <- gene_per_spec %>% 
  filter(name == 'P. australis', Orthogroup %in% groups_lost_in_P_australis) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_marina <- setdiff(groups_in_all_seagrasses, big_list[['Z. marina']])
genes_lost_in_Z_marina <- gene_per_spec %>% 
  filter(name == 'Z. marina', Orthogroup %in% groups_lost_in_Z_marina) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_muelleri <- setdiff(groups_in_all_seagrasses, big_list[['Z. muelleri']])
genes_lost_in_Z_muelleri <- gene_per_spec %>% 
  filter(name == 'Z. muelleri', Orthogroup %in% groups_lost_in_Z_muelleri) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()
```

>>>>

groups_lost_in_A_antarctica <- setdiff(groups_in_all_seagrasses, big_list[['A. antarctica']])
genes_lost_in_A_antarctica <- gene_per_spec %>% 
  filter(name != 'A. antarctica', Orthogroup %in% groups_lost_in_A_antarctica) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_P_australis <- setdiff(groups_in_all_seagrasses, big_list[['P. australis']])
genes_lost_in_P_australis <- gene_per_spec %>% 
  filter(name != 'P. australis', Orthogroup %in% groups_lost_in_P_australis) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_marina <- setdiff(groups_in_all_seagrasses, big_list[['Z. marina']])
genes_lost_in_Z_marina <- gene_per_spec %>% 
  filter(name != 'Z. marina', Orthogroup %in% groups_lost_in_Z_marina) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_muelleri <- setdiff(groups_in_all_seagrasses, big_list[['Z. muelleri']])
genes_lost_in_Z_muelleri <- gene_per_spec %>% 
  filter(name != 'Z. muelleri', Orthogroup %in% groups_lost_in_Z_muelleri) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()
```
